Ancestry linkage in hybrid zones

### 2016-02-03 drafts/hybrid_zone.tex
smaller selection figures
notes from talking to alisa

\paragraph{How fast do linked clines relax?}
Although loci not under selection can in principle spread across the cline unimpeded,
in practice it can take quite some time for even unlinked neutral loci to homogenize,
due to the decreased fitness of heterozygotes \citep{bartonbarrier}
and the relative slowness of diffusive movement \citep{sedghifar}.
Suppose we sample across at cline $\tau$ units of time after secondary contact.
How far away from the selected locus do we expect to see clines that have begun to flatten out more
than the selected cline?
A linked cline will have begun to flatten out if there is an appreciable chance that
a lineage at the linked locus initially linked to an $A$ allele 
at some point has recombined from an individual carrying the $B$ allele.
This implies that loci closer than $1/\tau$ to the selected site
certainly won't have a substantially wider cline than the selected cline.
\plr{Figure showing this?}
Of course, this calculation assumes that every generation provides an opportunity for recombination 
onto the other background,
but only recombinations in heterozygotes will move the linked lineage between selected backgrounds.
Since heterozygotes for the selected allele are only found at high frequency in the cline,
and lineages are generally pushed away from the cline but have no bias far away,
the amount of time a lineage spends in heterozygotes should grow as $\sqrt{\tau}$ for large $\tau$,
and so the width of the genomic region showing clines about the selected locus could be 
substantially larger than $1/\tau$.
However, this distinction appears hard to observe for realistic parameter values.

@@

%%%%%%
\begin{figure}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{figs/example_cline}
    \end{center}
    \caption{
        \textbf{Numerically computed clines,} at
        \textbf{(A)} the selected site, which forms over time $1/s$ and then remains stable, and
        \textbf{(B)} a linked site at distance $r=0.1$, which continues to smooth out as $\sqrt{t}$.
        Other parameters.
        \plr{Do we want this figure? This one is just a placeholder; I'd put in two, that showed the formation and spread better.
        Maybe putting in simulation results would be better, with comparison to numerical solutions? But, this is easier to look at?}
        \label{fig:pde_clines}
    }
\end{figure}

@@

%%%%%%
\begin{figure}
    \begin{center}
    \end{center}
    \caption{
        \textbf{Haplotype length distributions},
        comparing numerical solutions to simulations.
        \plr{maybe?}
        \label{fig:haplotype_lengths}
    }
\end{figure}

@@

>>>>

\paragraph{How fast do linked clines relax?}
Although loci not under selection can in principle spread across the cline unimpeded,
in practice it can take quite some time for even unlinked neutral loci to homogenize,
due to the decreased fitness of heterozygotes \citep{bartonbarrier}
and the relative slowness of diffusive movement \citep{sedghifar}.
Suppose we sample across at cline $\tau$ units of time after secondary contact.
How far away from the selected locus do we expect to see clines that have begun to flatten out more
than the selected cline?
A linked cline will have begun to flatten out if there is an appreciable chance that
a lineage at the linked locus initially linked to an $A$ allele 
at some point has recombined from an individual carrying the $B$ allele.
This implies that loci closer than $1/\tau$ to the selected site
certainly won't have a substantially wider cline than the selected cline.
\plr{Figure showing this? 
    For instance, either: (a) time-genome heatmap of number of heterozygotes (from PDE);
    or (b) a few time-space heatmaps of frequencies at different values of r (from PDE);
    or (c) a few space-genome heatmaps of frequencies at different times (from sims)
}
Of course, this calculation assumes that every generation provides an opportunity for recombination 
onto the other background,
but only recombinations in heterozygotes will move the linked lineage between selected backgrounds.
Since heterozygotes for the selected allele are only found at high frequency in the cline,
and lineages are generally pushed away from the cline but have no bias far away,
the amount of time a lineage spends in heterozygotes should grow as $\sqrt{\tau}$ for large $\tau$,
and so the width of the genomic region showing clines about the selected locus could be 
substantially larger than $1/\tau$.
However, this distinction appears hard to observe for realistic parameter values.

@@

%%%%%%
\begin{figure}
    \begin{center}
       \includegraphics[width=0.7\textwidth]{figs/example_cline}
    \end{center}
    \caption{
        \textbf{Numerically computed clines,} at
        \textbf{(A)} the selected site, which forms over time $1/s$ and then remains stable, and
        \textbf{(B)} a linked site at distance $r=0.01$, which continues to smooth out as $\sqrt{t}$.
        \textbf{(C)} a linked site at $r=0.1$
        \textbf{(D)} an unlinked site.
        Other parameters.
       \plr{Do we want this figure? This one is just a placeholder; I'd put in two, that showed the formation and spread better.
       This is from the PDE (we don't have time courses from sims).}
        \label{fig:pde_clines}
    }
\end{figure}

@@

%%%%%%
\begin{figure}
    \begin{center}
    \end{center}
    \caption{
        \textbf{Haplotype length distributions},
        comparing numerical solutions to simulations.
        At one time, plot 
        probability of seeing a haplotype of length at least $r$ covering that position on the genome,
        against (a) position on the genome, at a few spatial locations;
        or (b) spatial location, at a few positions on the genome.
        \plr{maybe?}
        \label{fig:haplotype_lengths}
    }
\end{figure}

@@

\subsection{Identifying sites under selection}

Plots with x-axis the genome and having peaks at the selected site.

Question: how much resolution do we have?
